---
title: "Retorno por data de aplicação"
subtitle: "Janeiro/2022"
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, middle

# Investimentos Estruturados 


```{r 1, message=FALSE, echo=FALSE,,warning=FALSE}
library(knitr)
library(readxl)
library(ggplot2)
library(tidyverse)
library(plotly)

setwd("C:\\Users\\Denilson\\Desktop\\Retorno\\base")

for (i in 1:12) {

  assign(list.files()[i],
         read_xlsx(list.files()[i],
                   col_types = c("date","numeric" ,"numeric","numeric","numeric","numeric","numeric","numeric")))
  
  assign(paste("g.",list.files()[i],sep=""),
         get(list.files()[i])%>%gather(indices,Retorno , -...1)%>%mutate(Data=as.Date(...1))%>%
           ggplot( aes(x = Data, y = Retorno, color = indices, group = indices)) +
           geom_line(size=1) +
           labs(title = paste("De",min(get(list.files()[i])$...1),"até",max(max(get(list.files()[i])$...1))))+
           theme(legend.position = "bottom", legend.title = element_blank())+
           scale_y_continuous("Retorno (em %)") +
           scale_x_date("Data", date_labels = "%m/%y", date_breaks = "6 month")+
           scale_color_brewer(palette = 'Dark2'))

  }

rm(i)

ggplot_Estr= list("Ibiúna Hedge STH"=g.IBIUNA.xlsx,
                  "GAP Absoluto"=g.GAP.xlsx,
                  "Novus Macro"=g.NOVUS.xlsx,
                  "Bahia AM Maraú"=g.BAHIA.xlsx,
                  "Bahia AM Maraú Estruturado"=g.BAHIAESTR.xlsx,
                  "Absolute Vertex II"=g.ABSOLUTE.xlsx)

ggplot_RV= list("Neo Navitas"=g.NEO.xlsx,
                "NAVI Institucional"=g.NAVI.xlsx,
                "VINCI MOSAICO"=g.VINCI.xlsx,
                "Constellation Institucional Advisory"=g.CONST.xlsx,
                "Moat Capital"=g.MOAT.xlsx,
                "Bradesco Selection"=g.BRADESCO.xlsx)

```

```{r create-markdown-chunks-dynamically, include=FALSE}

library(magrittr)

out = NULL
for (p_name in names(ggplot_Estr)) {
  knit_expanded <- paste0("\n\n---\n## Retorno ", p_name, "\n\n```{r results='asis', echo=FALSE, warning=FALSE,out.width = '800px', message=FALSE}\n\nggplotly(ggplot_Estr[['", p_name, "']])%>%layout(legend = list(orientation = 'h', x = 0.1, y = -0.2))\n\n```")
  out = c(out, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = out), collapse = '\n')`


---
class: center, middle

# Renda Variável

```{r create-markdown-chunks-dynamicall, include=FALSE}

library(magrittr)

out = NULL
for (p_name in names(ggplot_RV)) {
  knit_expanded <- paste0("\n\n---\n## Retorno ", p_name, "\n\n```{r results='asis', echo=FALSE, warning=FALSE,out.width = '800px', message=FALSE}\n\nggplotly(ggplot_RV[['", p_name, "']])%>%layout(legend = list(orientation = 'h', x = 0.1, y = -0.2))\n\n```")
  out = c(out, knit_expanded)
}
```

<!--- knit those table chunk statements --> 
`r paste(knit(text = out), collapse = '\n')`
